Sixty years of deforestation and forest degradation in Madagascar

### 2017-02-02 deforestmap.Rmd
Compute fragmentation

@@

We report an analysis of the evolution of forest fragmentation based on the forest-cover maps for Madagascar for the years 1953, 1973, 1990, 2000, 2010 and 2014. We used the approach developed by @Riitters2000 which uses a moving window to characterize the fragmentation around each forested pixel. We used a moving window of 3x3 pixels (0.81 km<sup2</sup>). Six categories of fragmentation are identified from the amount of forest and its occurrence as adjacent forest pixels: interior, perforated, edge, transitional, patch, and undetermined. The interior category can be interpreted as intact forest (see @Potapov2017). We reported the area of forest falling in each category for the 6 years and analysed the evolution of the fragmentation.

@@

@@

>>>>

Regarding the gains: we did not consider regrowth:
- few potential regrowth in Madagascar.
- regrowth are usually more easilly re-burnt for agriculture on the long term.
- young secondary forests do not provide the same ecosystem services (in terms of biodiversity and carbon storage) as old growth natural forests.

@@

We report an analysis of the evolution of forest fragmentation based on the forest-cover maps for Madagascar for the years 1953, 1973, 1990, 2000, 2010 and 2014. We used the method developed by @Riitters2000 which uses a moving window to characterize the fragmentation around each forested pixel. Computation were done using function `r.forestfrag` from GRASS GIS software. Six categories of fragmentation are identified from the amount of forest and its occurrence as adjacent forest pixels: interior, perforated, edge, transitional, patch, and undetermined. We used a moving window of 3x3 pixels (0.81 km<sup2</sup>). Using this window size, forest edge had a width of about 100m. The interior category can be interpreted as the most intact forest (sensus @Potapov2017). We reported the area of forest in each fragmentation category for the 6 years and analysed the evolution of the fragmentation with time.

@@

### 3.1 Validation

### 3.2 Evolution of forest cover, deforestation intensity and fragmentation with time

@@

### 4.1 Interest of such an approach

- simple
- easilly reproducible
- no need to define a tree cover threshold to
